TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
Added future work + discussion

\subsubsection{Traffic shaping based Monitoring}
With the use of a hypothetical TCP congestion control algorithm that is unfair to other TCP congestion control algorithms, the bandwidth allocation to one customer can be higher to other customers using the default congestion control algorithms. For example: when a TCP congestion control algorithm shows an aggressive increase and keeps pushing data over the network, other fair TCP congestion algorithms will reduce the sending rate of the data transfer as packet loss occurs. One important condition for this unfair congestion control algorithm is that it should not be that agressive such that it behaves in a Denial of Service manner.

@@

\section{Discussion}\label{sec:discussion}

\section{Conclusion}\label{sec:conclusion}
To do: Monitoring $\alpha$ value research. future work.

>>>>

\subsubsection{Traffic shaping based Monitoring}
With the use of a hypothetical TCP congestion control algorithm that is unfair to other TCP congestion control algorithms, the bandwidth allocation to one customer can be higher than for other customers using the default congestion control algorithms. For example: when a TCP congestion control algorithm shows an aggressive increase and keeps pushing data over the network, other fair TCP congestion algorithms will reduce the sending rate of the data transfer as packet loss occurs. One important condition for this unfair congestion control algorithm is that it should not be that agressive such that it behaves in a Denial of Service manner.

@@

\section{Discussion}\label{sec:discussion}
The CTCP measurements were done on a Windows 10 machine. All other measurements were done on machines running Ubuntu 17.04. This might have introduced issues while measuring the CTCP algorithm versus any other congestion algorithm. CTCP did not show the expected behavior when running the tests. According to our measurements, all other algorithms are fair in sharing bandwidth with other algorithms. However, all measurements from CTCP show different results. We think this might be caused by the way Python sockets or Python calls are handled in Windows 10. We have performed the 0\% loss 0ms delay test on different hardware, which resulted in the same low value of bandwidth usage. When we used \texttt{iperf}, it reached the half of 1 Gbps versus other congestion algorithms as expected. We also increased the amount of bytes sent each time, where it reached 1 Gbps on its own. However, when testing it against another congestion algorithm it still showed the same behavior: performing with a low throughput. Therefore, we think the call handling of Python in Windows encounters more delay than Linux, but this requires more testing.

\section{Future work}\label{sec:futurework}
Running a mixed environment of Linux and Windows where Python is running introduces issues. We expect the call handling of Python in Windows encounters more delay than in Linux, but this requires more testing. The tests for CTCP might have to be performed again when full speeds can be reached by using the same settings. 
The CTCP tests are currently executed on Windows 10. This might also be performed on a Windows Server instance as it possibly handles the network in a different way.

All tests described in this paper can be performed with more parallel connections, so that even when using a lot of parallel connections with two different congestion control algorithms, it is proven that the congestion control algorithms are fair.

In this paper we have proposed a monitoring solution, which checks for the deviation between the server bandwidth on a link and the average bandwidth used by servers on a link. This solution requires performance testing, such that it is capable of running in a datacenter and not causing delay. Also an $\alpha$ value has to be determined that works in most environments, without ruling out servers that are not running unfair TCP congestion protocols.

\section{Conclusion}\label{sec:conclusion}
To do: Mention items:
\begin{enumerate}
	\item{With current TCP congestion control algorithms behaving fair: No traffic control is currently needed & there is no impact on service and availability for customers}
	\item{BBR is best performing algorithm of five tested}
	\item{DCTCP is only suitable when both server and client are in same datacenter}
	\item{Windows needs further testing}
\end{enumerate}
